Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models

### 2018-09-28 paper.tex
.

\documentclass[preprint,5p,times,twocolumn,authoryear,draft]{elsarticle}

@@

\begin{table*}
	\caption{\added{\textbf{Summary statistics of different distances for schelling.}}}\label{tab:schellingdistances}
	\centering
	\begin{tabular}{|ccccccc|}
	\hline
    	$q$ & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\\hline
        1 & 0.00000 & 0.02838 & 0.06263 & 0.10608 & 0.16818 & 0.37018 \\
        2 & 0.0000 & 0.1520 & 0.2517 & 0.3107 & 0.4359 & 0.8155 \\
        3 & 0.0000 & 0.3709 & 0.5133 & 0.5860 & 0.7435 & 1.2930 \\
        10 & 0.000 & 2.083 & 2.431 & 2.380 & 2.713 & 3.664 \\\hline
    \end{tabular}
\end{table*}

\begin{table*}
	\caption{\added{\textbf{Summary statistics of different distances for sugarscape.}}}\label{tab:sugarscapedistances}
	\centering
	\begin{tabular}{|ccccccc|}
	\hline
    	$q$ & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\\hline
        1 & 0.07184 & 0.13996 & 0.39816 & 0.42452 & 0.64751 & 1.13169\\
        2 & 0.08909 & 0.19794 & 1.52272 & 1.29594 & 2.16371 & 2.98273\\
        3 & 0.1025 & 0.2288 & 3.1495 & 2.5074 & 4.2718 & 5.5378\\
        10 & 0.1540 & 0.4466 & 9.8757 & 7.6246 & 13.0550 & 16.8001\\\hline
    \end{tabular}
\end{table*}

@@

%%%%%%%%%%%%%%%
\begin{figure*}
% Minimal netlogo code for the sugarscape model
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the sugarscape model.} Conventions are the same than for Schelling pseudo-code.}}
\begin{mdframed}
\begin{lstlisting}
while [time < final-time] [
;regrow the patch resources
    ask patches [set psugar min (list max-psugar (psugar + 1))]

	; make agents exploit resources
	ask turtles [
		; candidate patches to which the turtle can move
		let move-candidates (*@\textit{patches in vision range with no turtles}@*)

>>>>

\documentclass[preprint,5p,times,twocolumn,authoryear]{elsarticle}

@@

\begin{table*}
	\caption{\added{\textbf{Summary statistics of different distances for schelling.}}}\label{tab:schellingdistances}
	\centering
	\begin{tabular}{|c|cccccc|}
	\hline
    	$q$ & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\\hline
        1 & 0.00000 & 0.02838 & 0.06263 & 0.10608 & 0.16818 & 0.37018 \\
        2 & 0.0000 & 0.1520 & 0.2517 & 0.3107 & 0.4359 & 0.8155 \\
        3 & 0.0000 & 0.3709 & 0.5133 & 0.5860 & 0.7435 & 1.2930 \\
        10 & 0.000 & 2.083 & 2.431 & 2.380 & 2.713 & 3.664 \\\hline
    \end{tabular}
\end{table*}

\begin{table*}
	\caption{\added{\textbf{Summary statistics of different distances for sugarscape.}}}\label{tab:sugarscapedistances}
	\centering
	\begin{tabular}{|c|cccccc|}
	\hline
    	$q$ & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\\hline
        1 & 0.07184 & 0.13996 & 0.39816 & 0.42452 & 0.64751 & 1.13169\\
        2 & 0.08909 & 0.19794 & 1.52272 & 1.29594 & 2.16371 & 2.98273\\
        3 & 0.1025 & 0.2288 & 3.1495 & 2.5074 & 4.2718 & 5.5378\\
        10 & 0.1540 & 0.4466 & 9.8757 & 7.6246 & 13.0550 & 16.8001\\\hline
    \end{tabular}
\end{table*}

@@

%%%%%%%%%%%%%%%
\begin{figure*}
% Minimal netlogo code for the sugarscape model
\caption{\added{\textbf{Pseudo-code (NetLogo style) for the sugarscape model.} Conventions are the same than for Schelling pseudo-code.}}
\begin{mdframed}
\begin{lstlisting}
while [time < final-time] [
    ask patches [set psugar min (list max-psugar (psugar + 1))]
	ask turtles [
		; candidate patches to which the turtle can move
		let move-candidates (*@\textit{patches in vision range with no turtles}@*)
